Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
Pass on Section 8

\begin{enumerate}
\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
  should be encouraged;
\item The cost of inspection of the warnings in differential testing
  should be reduced;
\item Finding bugs in large software is a very effective way to engage
  student in contributing to open-source software and learning
  Software Testing practices.
\end{enumerate}

>>>>

\begin{enumerate}
\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
  should be encouraged;
\item The cost of inspection of the warnings in differential testing
  should be reduced;
\item Finding bugs in large software is a very effective way to engage
  students in contributing to open-source software and learning
  Software Testing practices.
\end{enumerate}
